Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-12-07 latex/paper.tex
添加郭志新提出的refrence

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-22 14:17:59

@@

Many theoretical and experimental results have shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them great potential in the applications of thermoelectrics. For example, the experiment of Boukai \emph{et al}.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values of approximately 100-fold improvement over bulk Si are achieved over a broad temperature range. Hochbaum \emph{et al}.\cite{Hochbaum2008} also proposed a way of increasing ZT by controling the roughness of silicene nanowires. At present, the thermal conductivity of the silicon nanostructures, i. e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a} \textbf{Add, J. Phys.: Condensed Matter 28, 145003 (2016)} had been well studied. However, the thermal conductivity of multilayer silicene is still mysterious.  
The combined effects of quantum size and surface reconstruction in multilayer silicene is expected to induce exotic thermal transport properties different from both monolayer silicene and bulk Si,  which may make it suitable for the thermoelectric applications. Since the the thermal conductivity of monolayer silicene and  bulk Si have been well explored, investigation on multilayer silicene is also helpful for understanding the thermal conductivity  evolution from two dimensional (2D) to three dimensional (3D) systems.

The existing research on thermal conductivity of  2D materials  mainly focus on the ones with weak Van der Waals(vdW) interlayer interaction where there is no surface reconstruction, such as multilayer graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015}.  Whereas, the thermal conductivity of 2D materials with strong interlayer interactions have been barely explored.
The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation\cite{}\textbf{ [add more refs on mutilayer silicene, such as Appl. Phys. Lett. 102, 163106 (2013); Appl. Phys. Lett. 104, 131904 (2014),Guo2015Structural}. 
Previous studies  showed that the mutilayer silicene exhibit special surface reconstructions which induces the intriging electronic properties ( \textbf{ Ref. Appl. Phys. Lett. 104, 131904 (2014), Guo2015Structural}. Naturally, one can expect that  the surface reconstruction is a significant factor for the thermal conductivity. 
Especially, revealing the surface reconstruction effect on thermal conductivity anisotropy  in mutilayer silicene  promotes the applications of covalently bonded 2D materials in the thermoelectrics.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-12-07 14:28:22

@@

Many theoretical and experimental results have shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them great potential in the applications of thermoelectrics. For example, the experiment of Boukai \emph{et al}.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values of approximately 100-fold improvement over bulk Si are achieved over a broad temperature range. Hochbaum \emph{et al}.\cite{Hochbaum2008} also proposed a way of increasing ZT by controling the roughness of silicene nanowires. At present, the thermal conductivity of the silicon nanostructures, i. e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a,Chen2016} had been well studied. However, the thermal conductivity of multilayer silicene is still mysterious.
The combined effects of quantum size and surface reconstruction in multilayer silicene is expected to induce exotic thermal transport properties different from both monolayer silicene and bulk Si,  which may make it suitable for the thermoelectric applications. Since the the thermal conductivity of monolayer silicene and  bulk Si have been well explored, investigation on multilayer silicene is also helpful for understanding the thermal conductivity  evolution from two dimensional (2D) to three dimensional (3D) systems.

The existing research on thermal conductivity of  2D materials  mainly focus on the ones with weak Van der Waals(vdW) interlayer interaction where there is no surface reconstruction, such as multilayer graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015}.  Whereas, the thermal conductivity of 2D materials with strong interlayer interactions have been barely explored.
The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation
\cite{Fu2014,Padova2016,Guo2015Structural}.
Previous studies  showed that the mutilayer silicene exhibit special surface reconstructions which induces the intriging electronic properties\cite{Fu2014,Guo2015Structural}. Naturally, one can expect that  the surface reconstruction is a significant factor for the thermal conductivity.
Especially, revealing the surface reconstruction effect on thermal conductivity anisotropy  in mutilayer silicene  promotes the applications of covalently bonded 2D materials in the thermoelectrics.
